---
title: "Class-activity-1"
author: "Aidi"
date: "9/20/2018"
output: html_document
---
### Instructions
  
1. Open a new R Markdown file, please write and run all your commands from within the R Markdown document  
2. Delete the contents of the Markdown file and insert a new code block
3. Load the libraries  `tidyr` and `dplyr`
4. Create a data frame from the `swirl-data.csv` file called `DF1`

```{r}
library(dplyr)
library(tidyr)
DF1<-read.csv("/Users/aidibian/Documents/2018 FALL/# Classes/HUDK 4050/class4/class-activity-1/swirl-data.csv",header = TRUE)
```


The variables are:

`course_name` - the name of the R course the student attempted  
`lesson_name` - the lesson name  
`question_number` - the question number attempted
`correct` - whether the question was answered correctly  
`attempt` - how many times the student attempted the question  
`skipped` - whether the student skipped the question  
`datetime` - the date and time the student attempted the question  
`hash` - anonymyzed student ID  

5. Create a new data frame that only includes the variables `hash`, `lesson_name` and `attempt` called `DF2`
```{r}
DF2 <- DF1 %>%
  select(hash, lesson_name, attempt)
```

6. Use the `group_by` function to create a data frame that sums all the attempts for each `hash` by each `lesson_name` called `DF3`
```{r}
DF3<-DF2%>%
  group_by(hash, lesson_name) %>%
  summarise(sum = sum(attempt))
```


7. On a scrap piece of paper draw what you think `DF3` would look like if all the lesson names were column names

8. Convert `DF3` to this format  
```{r}
spread(DF3, lesson_name, sum)
```

9. Create a new data frame from `DF1` called `DF4` that only includes the variables `hash` and `correct`
```{r}
DF4<-DF1%>%
  select(hash, correct)
```


10. Convert the `correct` variable so that `TRUE` is coded as the **number** `1` and `FALSE` is coded as `0`  
```{r}
DF <- na.omit(DF4)
DF4<-DF4%>%
  mutate(correct = ifelse(correct == TRUE, 1, 0))
# or: DF4$correct<-ifelse(DF4$correct == TRUE, 1, ifelse(DF4$correct == NA, NA, 0))
# to see whether there is NA
table(DF4$correct)
hist(DF4$correct)
summary(DF4$correct)
```


11. Create a new data frame that called `DF4` that provides a mean score for each student
```{r}
DF4_mean<-DF4%>%
  filter(!is.na(correct1))%>%
  group_by(hash)%>%
  summarise(mean=mean(correct1, na.rm = TRUE))
```


12. **Extra credit** Convert the `datetime` variable into month-day-year format and create a new data frame (`DF5`) that shows the average correct for each day


```{r}
DF5 <- DF1 %>%
  mutate(datetime1 = as.Date.POSIXct(DF1$datetime), correct1 = ifelse(correct == TRUE, 1, 0))
DF5$datetime<-as.POSIXct(DF5$datetime1, origin = "1970-01-01 00:00:00 UTC")
DF5 %>%
  filter(!is.na(correct1))%>%
  group_by(datetime1) %>%
  summarise(avg_correct = mean(correct1))
```

```{r}
DF6 <- select(DF1, correct, datetime)

DF6$correct <- ifelse(DF6$correct == TRUE, 1, 0)

DF6$datetime <- as.POSIXlt(DF6$datetime, origin = "1970-01-01 00:00.00 UTC")

DF6$datetime <- strftime(DF6$datetime, format="%b:%e")

DF7 <- DF6 %>% group_by(datetime) %>% summarise(av.correct = mean(correct, na.rm = TRUE))
```

